---
title: 'Contrived scale line as a collapsaro: evidence from China stock market''s
  price limit rules'
output: 
  pdf_document:
    dev: cairo_pdf
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(cnquant)
library(knitr)
library(kableExtra)
load("../data/01-D-First-Complete-Data.RData")
options(knitr.kable.NA = "-")
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
theme_set(
  theme_minimal(base_size = 11, base_family = "STSong") + 
    theme(
      legend.position = c(1, 1), 
      legend.justification = c(1, 1), 
      legend.spacing = unit(8, "pt"), 
      legend.box = "horizontal", 
      legend.title = element_text(size = 10), 
      legend.text = element_text(size = 8), 
      legend.background = element_rect(fill = "white", colour = FALSE)
    )
)
```

# Introduction

In am ideal frictinoles stock market, stock price walks randomly. Actually, howerver, does any price really makes the same sense in terms of probability? For instance, a round number may impress people more than a none-round number, thus \$100 other than \$94.56 may makes a difference psychologically to a investor. The question comes that will this difference affect the price trend practically? In China's stock market, the two exchanges, Shanghai Stock Exchange (SSE) and the Shenzhen Stock Exchange (SZSE), restrict the daily absolute movement of a stock price to 10% of the previous trading day’s closing price for most of their listed stocks, thus the upper and lower price limit equivalent to 10% and -10%[^1] may make special to investors, which has provided fantastic source material to test the effect of contrived price scale line.

[^1]: Actully because the minimum tick size for stocks is RMB one cent. Therefore, in cases where a 10% price change is not an integral number of cents, the daily price limit is rounded to the nearest cent.

Thus, we focus on extreme stock price movements that approach the upper or lower limit. The


Distribution of maximum and minimum daily price percent change

```{r high_pctchange_dist, message=FALSE}
# 日最大收益率的分布
p1 <- Stock_Daily_Data0 %>% 
  mutate(HIGH_PCTCHANGE = S_DQ_HIGH / S_DQ_PRECLOSE - 1) %>% 
  ggplot(aes(x = HIGH_PCTCHANGE)) +
  geom_histogram(binwidth = 0.0001) + 
  scale_x_continuous(labels = percent) + 
  coord_cartesian(ylim = c(0, 5000)) + 
  labs(x = "Maximum price percent change in the day", 
       y = "Count")
p1_zoom <- p1 + 
  coord_cartesian(xlim = c(0.08, 0.1), ylim = c(0, 5000))

p2 <- Stock_Daily_Data0 %>% 
  mutate(LOW_PCTCHANGE = S_DQ_LOW / S_DQ_PRECLOSE - 1) %>% 
  ggplot(aes(x = LOW_PCTCHANGE)) +
  geom_histogram(binwidth = 0.0001) + 
  scale_x_continuous(labels = percent) + 
  coord_cartesian(ylim = c(0, 5000)) + 
  labs(x = "Minimum price percent change in the day", 
       y = "Count")
p2_zoom <- p2 + 
  coord_cartesian(xlim = c(-0.1, -0.08), ylim = c(0, 5000))

Rmisc::multiplot(p1, p1_zoom, p2, p2_zoom, cols = 2)
```

```{r}
basic_count <- tibble(
  Type = c("All", "Upper", "Lower"), 
  `Obs. All` = nrow(Stock_Daily_Data0), 
  `Obs. Reach 9%` = c(Stock_Daily_Data %>% nrow(), 
                      Stock_Daily_Data %>% filter(REACH_UP_THRESHOLD) %>% nrow(), 
                      Stock_Daily_Data %>% filter(REACH_DOWN_THRESHOLD) %>% nrow()), 
  `Obs. Reach Limit` = c(Stock_Daily_Data %>% filter(REACH_UP_LIMIT | REACH_DOWN_LIMIT) %>% nrow(), 
                         Stock_Daily_Data %>% filter(REACH_UP_LIMIT) %>% nrow(), 
                         Stock_Daily_Data %>% filter(REACH_DOWN_LIMIT) %>% nrow())
) %>% 
  mutate(`Prob. Reach 9%` = `Obs. Reach 9%` / `Obs. All`, 
         `Prob. Reach Limit` = `Obs. Reach Limit` / `Obs. All`, 
         `Con. Prob. Reach Limit` = `Prob. Reach Limit` / `Prob. Reach 9%`) %>% 
  mutate_at(vars(`Prob. Reach 9%`:`Con. Prob. Reach Limit`), formattable::percent, digits = 1L)

basic_count %>% 
  kable(format.args = list(big.mark = ","), 
        booktabs = TRUE) %>% 
  kable_styling(latex_options = "scale_down")
```


# Data and methodology

## methodology

Stock price movement is commonly presumed to follow a geometric Brownian motion (GBM). Let $S$ be the stock price at time $t$, it's disrete time form is 
$$\frac{\Delta S}{S} = \mu \Delta t + \sigma \epsilon \sqrt{\Delta t}$$
or 
$$\Delta S = \mu S\Delta t + \sigma S \epsilon \sqrt{\Delta t}$$
Variable $\Delta S$ is the stock price change after a short time period $\Delta t$. $\epsilon$ follows a starndart normal distribution, whose expectaion is 0 and variance is 1. Parameter $\mu$ is the expected return of the stock in unit time while parameter $\sigma$ is the volatility rate of the stock, both of which are assumed to be constants.
The equation indicates that $\Delta S / S$ follows a normal distribution whose expection is $\mu \Delta t$ and standard deviation is $\sigma \sqrt{\Delta t}$. That is 
$$\frac{\Delta S}{S} \sim \phi(\mu \Delta t, \sigma^2 \Delta t)$$
When $t \to 0$, we get the continuous time form
$$\frac{dS}{S} = \mu dt + \sigma dz$$
or
$$dS = \mu Sdt + \sigma Sdz$$
where $z$ is Brownian motion.

## A MCMC approach
The Monte Carlo simulatin of a stochastic process is a precedure to cast repititive random sampling of the process. The simulation process involves two parameters $\mu$ and $\sigma$. We estimate the parameters with historical stock price data. We use a 120 day rolling window for estimating the parameters of the day. Then we cast MCMC simulation.

### Diagram


# Baseline results

```{r}
base_up <- Stock_Daily_Data4_UP %>% 
  summarise(REACH_LIMIT_mean = mean(REACH_UP_LIMIT), 
            PROB_REACH_LIMIT_mean = mean(PROB_REACH_UP_LIMIT, na.rm = TRUE), 
            diff = REACH_LIMIT_mean - PROB_REACH_LIMIT_mean, 
            p.value = t.test(REACH_UP_LIMIT, PROB_REACH_UP_LIMIT)$p.value)
base_down <- Stock_Daily_Data4_DOWN %>% 
  summarise(REACH_LIMIT_mean = mean(REACH_DOWN_LIMIT), 
            PROB_REACH_LIMIT_mean = mean(PROB_REACH_DOWN_LIMIT, na.rm = TRUE), 
            diff = REACH_LIMIT_mean - PROB_REACH_LIMIT_mean, 
            p.value = t.test(REACH_DOWN_LIMIT, PROB_REACH_DOWN_LIMIT)$p.value)
bind_rows(base_up, base_down) %>% 
  mutate_at(vars(REACH_LIMIT_mean:diff), formattable::percent, digits = 1L) %>% 
  kable(booktabs = TRUE) %>% 
  kable_styling(position = "center")
```




## Robustness: daily v.s. intraday estimate


# Hard-to-Value Firms


# Investor Sentiment


