---
title: "Contrived Price Line as A Collapsaro: Evidence from China Stock Market's
  Price Limit Rules"
abstract: We verify the magnet effect of contrived scale line of stock price 
  based on prospective of probabilities with upper and lower price limit in 
  China's stock market. We find that magnet effect is stronger for 
  harder-to-value firms and more avtive-trading firms. We show that a stimulus 
  is necessay to trigger the magnet effect. Future liquidity concerns of 
  institutional investors may be the driving factor behind the scene.
output: 
  pdf_document:
    dev: cairo_pdf
    number_sections: yes
    latex_engine: xelatex
fontsize: 12pt
bibliography: references.bib
# header-includes:
# - \usepackage[fontsize=15pt]{scrextend}
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)
library(cnquant)
library(knitr)
library(kableExtra)
library(formattable)
library(scales)
library(stargazer)
load("../data/02-D-For-Rmd-Paper.RData")
options(digits = 2L, 
        scipen = 99, 
        knitr.kable.NA = "-")
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
theme_set(
  theme_minimal(base_size = 11) + 
    theme(
      # legend.position = c(1, 1), 
      # legend.justification = c(1, 1), 
      legend.spacing = unit(8, "pt"), 
      legend.box = "horizontal", 
      legend.title = element_text(size = 10), 
      legend.text = element_text(size = 8), 
      legend.background = element_rect(fill = "white", colour = FALSE)
    )
)
Sys.setlocale("LC_TIME", "en_US.UTF-8")
start_date <- start_date %>% ymd() %>% format("%b %d %Y")
end_date <- end_date %>% ymd() %>% format("%b %d %Y")
```


# Introduction

In an ideal frictionless stock market, stock price walks randomly. The probability to go to another price depends on how far away that price is from the current one. The farther, the less likely, while it does no matter what the exact price is. Howerver, do different prices really make the same sense in terms of other than probability, given the truth that people may pay more attention to some particular price line like rounding numbers or other contrived ones? For example, \$100 relative to \$94.56 may indeed means something different to investors. The question comes that will this difference affect the price trend practically? In China's stock market, the two exchanges, Shanghai Stock Exchange (SSE) and the Shenzhen Stock Exchange (SZSE), restrict the daily absolute movement of a stock price to 10% of the previous trading day’s closing price for most of their listed stocks, thus the upper and lower price limit equivalent to 10% and -10%[^1] may make special to investors, which has provided fantastic source material to test the effect of contrived price scale line.

[^1]: Actully because the minimum tick size for stocks is RMB one cent. Therefore, in cases where a 10% price change is not an integral number of cents, the daily price limit is rounded to the nearest cent.

While much attention has been paid on the distribution on stock returns, seldom has been paid to the maximum ones. The top two subfigures of Figure \ref{fig:extreme_dist} displays the daily maximum and minimum returns distribution all stocks listed within China. The distributions come nothing than a common normal or student-t distribution, but have unusual multimodal forms. For the maximum side, for example, first, a descent proportion stays right at the zero point for stocks not having any price change during the day. Second, there are two peak not far away from the zero point at positive and negative respectly. Last but not least, a huge numbern of points accumulate at arround the 10% change. When we zoom in at here (the bottom subfigures), we even see an incremental trend towards the 10% scale line, which can be surprising given the truth that the previous trend decays.

We will focus on these extreme stock price movements that approach the upper or lower limit through this paper.

```{r extreme_dist, fig.pos="H", fig.cap="Distribution of Maximum and Minimum Daily Price Percent Changes"}
Rmisc::multiplot(p_Max_Dist, p_Max_Dist_Zoom, p_Min_Dist, p_Min_Dist_Zoom, cols = 2L)
```

There are `r Extreme_Prop[1, 3]` out of `r Extreme_Prop[1, 2]` stock-day observations having reached a 9% price change with a probability of `r Extreme_Prop[1, 5]`, and `r Extreme_Prop[1, 4]` out of `r Extreme_Prop[1, 2]` stock-day observations having reached the 10% price limit with a probability of `r Extreme_Prop[1, 6]`, while the conditional probability is `r Extreme_Prop[1, 7]` (see Table \ref{tab:extreme_prop}). We have excluded obserbations when the open price is at the price limit, because these observations will have no more price movement the whole day. The conditional probability seems to be large, but there's no benchmark for it to be compared from.

```{r extreme_prop}
Extreme_Prop %>% 
  mutate_at(vars(`Prob. Reach 9%`:`Con. Prob. Reach Limit`), 
            formattable::percent, digits = 1L) %>% 
  kable(caption = "Number of Observations Reaching 9\\% and 10\\% Price Changes", 
        format.args = list(big.mark = ","), 
        booktabs = TRUE) %>% 
  kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

All these concerns inspired us to verify whether there exists such a "magnet effct" at the price scale lines from the prospective of probabilities.

In order to verify our conjecture, from the perspective of probabilities, that 
there exists a magnet effect of price limits when stock price goes close to 
them, we need to compare the practical conditional probability of stock 
price's reaching the price limit when having achieved some close level, to a 
theoretical benchmark. It is commonly asssumed that the stock price follows 
geometric Brownian motion (GBM) [@Black:1973aa]. We adopt the GBM model to the 
stock price 
process at the time it crosses the threshold level. Since the stock price is a 
markov process, we can obtain the probability it will reach the price limit 
from then on during that day with the stock price's drift rate $\mu$ and 
volatiliy rate $\sigma$ parameters. We ascertain the pinpoint time when stock 
price crosses the threshold with intraday tick data and estimate the two 
necessary model parameters with historical stock prices and returns. The 
calculation workhorse of theoretial probability whether the stock price is 
able to reach the price limit is via a Markov Chain Monte Carlo (MCMC) 
approach.

We calculate the theoretical probability for each stock-day that the stock 
price has ever reached a percentage change of a close threshold (for example, 
±9%) respectively for the upper and lower direction. The calculation involves 
huge intense computation and we believe to be the first one to do such 
comprehensive work. 

The result shows that there is fairly a huge gap betweent the practical 
empirical probability and the mean theoretical probability, with the former 
one sitting upon the latter one, which shows the magnet effect of price limits 
we state.

We next examine that the magnet effect is greater for harder-to-value firms and 
those with more active trading activitys. We use a number of different proxies 
to measure the extent to which a firm’s shares are difficult to value: firm 
size, price-to-earnings ratio, whether paying dividend and 
price-to-dividend ratio. Firms that are more smaller, less profitable, and 
paying no or less dividend are likely to be harder to value. We do a logistic 
regression on the probability to reach price limit with each hard-to-value 
measure controling mainly for the theoretical probability. For each measure, 
as is expected, the magnet effect tends to be significantly stronger for the 
more-difficult-to-value firm than the less-difficult-to-value firms.

We test for the effect of individual stock trading dynamism on magnet effect by 
running logistic regressions depending on various measures including trading 
volume in RMB and turnover ratio. As expected, the magnet effect turns 
stronger when stock trading dynamism increases. The coefficients are all 
reliably significant.

Next, we examine whether a stimulus is necessary to trigger the magnet effect. 
That is, there is a incresing process of the stock price to approach the price 
limit. We compare sample of those who have got a large overnight return beyond 
threshold with those whose price crosses the threshold during daylight 
continuous auctions. The sample without a trigger has got a much higher 
theoretical probability since the longer time promises a larger volatility 
arrange. The practical probability comes also a little higher, however, the 
difference tends to be insignificant. This suggests that a signal during 
trading is a necessary trigger for the magnet effect.

To gain insight of the emergence of the magnet effect, we state that it may be 
caused by liqudity concerns especially by institutional invesetors. When stock 
price reaches price limit, the stock will be no longer tradable (at that 
direction). For that sake, when it approaches the price limit, institutional 
investors may trade it in advance to avoid possible future illiquidity. We 
regress the probability on institutional holding and the result turns out to 
be that firms with larger institutional holdings have a stronger magnet effect.

The remaining of the paper is structured as follows: section 
\ref{data-and-methodology} introduce the data we use and methodology we adopt, 
section \ref{baseline-result} shows the baseline result, section 
\ref{further-analysis} carries out some further analysis, section 
\ref{possible-explanation} gives out some possible explanation, and section 
\ref{conclusion} concludes the paper.


# Data and Methodology

## Data

Our primary data source is the Wind financial database which is the most 
comprehensive and powerful database in China stock market. We include all 
common shares listed in SSE and SZSE, including all of the mainboard, small 
and medium enterprise board and growth stock board. Our sample spans from 
`r start_date` to `r end_date`, for we have only access to high frequentcy 
stock database during this period. We construct our sample with stock-day that 
the stock price crosses a certain threshold (for example, ±9%) at that day. We 
exclude stock-day that the stock is temporally halted from trading or newly 
listed within 3 months. In addition, there are a special proportion of stocks 
marked as ST (special treated), which have often met a deficit for consecutive 
3 years and are facing delisting off board. These special stocks have a 
special 5% price limit other than normal ones and we exclude them as well.


## Methodology

### Geometric Brownian Motion

Stock price movement is commonly presumed to follow a geometric Brownian motion (GBM). Let $S$ be the stock price at time $t$, it's disrete time form is 
$$\frac{\Delta S}{S} = \mu \Delta t + \sigma \epsilon \sqrt{\Delta t}$$
or 
$$\Delta S = \mu S\Delta t + \sigma S \epsilon \sqrt{\Delta t}$$
Variable $\Delta S$ is the stock price change after a short time period $\Delta t$. $\epsilon$ follows a starndart normal distribution, whose expectaion is 0 and variance is 1. Parameter $\mu$ is the expected return of the stock in unit time while parameter $\sigma$ is the volatility rate of the stock, both of which are assumed to be constants.
The equation indicates that $\Delta S / S$ follows a normal distribution whose expection is $\mu \Delta t$ and standard deviation is $\sigma \sqrt{\Delta t}$. That is 
$$\frac{\Delta S}{S} \sim \phi(\mu \Delta t, \sigma^2 \Delta t)$$
When $t \to 0$, we get the continuous time form
$$\frac{dS}{S} = \mu dt + \sigma dz$$
or
$$dS = \mu Sdt + \sigma Sdz$$
where $z$ is Brownian motion.

### An MCMC Approach

To obtain the theoretical probability of stock price's reaching the price 
limit conditional on having reached some threshold, we first need to ascertain 
the exact time that stock price crosses the threshold, and then calculate the 
probability it hit the price limit throughtout the remaining day. For the 
majority part of our paper, we set the threshold to be ±9% and we also discuss 
the circumstance of different thresholds. We ascertain the pinpoint time with 
the precision of three seconds via the intraday tick quotes data. Then we 
apply the GBM model to the stock price and adopt the MCMC method as workhorse. 
Specifically, we first estimate the drift rate $\mu$ and volatility rate 
$\sigma$ with a rolling window of stock's past 1 year's returns. Then we 
simulate as many as 1000 trajectory paths since the stock price crosses the 
threshold during the day. We record for each trajectory whether it reaches the 
price limit, and use the empirial frequency as the estimator of the 
theoretical probability.

```{r exam_traj, fig.pos="H", fig.cap="Illustration of the MCMC Simulation"}
p_Exam_Traj
```

\ref{fig:exam_traj} illustrates the simulation process for one observation. 
The stock price of PingAn Bank (tick symbol code "000001", listed on SZSE) 
crosses the +9% threshold of ¥12.33 at 13:13:03 on 
`r Stock_Daily_Data3$UP$TRADE_DT[1] %>% ymd() %>% format("%b %d %Y")`. The 
pre-close price is ¥11.31, thus the upper price limit is ¥11.31 * (1 + 10%) 
equals ¥12.44. We then use the GBM parameters $\mu$ and $\sigma$, estimated 
with the historical stock prices data before, to simulate 1000 trajectories 
presumed with no price limit from 13:13:03 on (Figure \ref{fig:exam_traj} 
displays only 10 trajectories for example for the sake of concisement). The 
proportion out of all 1000 trajectories that reaches the ¥12.44 upper price 
limit is recorded to obtain the probability. The probability in 
\ref{fig:exam_traj} is 20% (2 out of 10) here, while the actuall process 
involves a simulation of as many as 1000 trajectories for each sample 
observation which is able to carry out an accurate result.


# Baseline Result

Our sample contains all stock-day that the stock price has ever reached an +9% 
or -9% change. Some observatins has hit the upper or lower price limit 
iniatially at the market opening, thus have a "---" shape the whole day. We 
exclude these observations because they have no price variation during the day 
at all. About 3.9% and 4.1%, respectively, of observations have reached the +9%
and -9% thresholds. We then exclude observations with missing intraday data 
couterpart. The final samples have a size of `r Prac_Vs_Theo[2, 7]` for the 
upper direction, and `r Prac_Vs_Theo[3, 7]` for the lower direction 
respectively. We also have a aggregated sample consists of both the upper and 
lower samples.

In Table \ref{tab:prac_vs_theo} we show the simulated mean theoretical 
probability that the stock price reach the price limit conditional on having 
reached a 9% threshold, as well as the practical probability that the stock 
price actually hit the price limit. In the aggregated sample which contains 
both the two direction samples, the theoretially mean probability is 
`r Prac_Vs_Theo[1, 3]` while the actuall probability is `r Prac_Vs_Theo[1, 2]`.
The difference is `r Prac_Vs_Theo[1, 4]` which is significant at the 1% level.

```{r prac_vs_theo}
Prac_Vs_Theo %>% 
  mutate_at(vars(`Prac. Prob.`:Diff.), formattable::percent, digits = 1L) %>%
  kable(caption = "Probability of Reaching Price Limit -- Practically V.S. Theoretically", 
        digits = 1L, 
        format.args = list(big.mark = ","), 
        booktabs = TRUE) %>% 
  kable_styling(latex_options = "HOLD_position")
```

When we look at the two directions separately, the upper one has a practical 
probability of `r Prac_Vs_Theo[2, 2]` and a theoretical probability of 
`r Prac_Vs_Theo[2, 3]`. The difference is `r Prac_Vs_Theo[2, 4]` significant 
at 1% level. As for the lower direction, the theoretical probability is 
`r Prac_Vs_Theo[3, 3]`, much lower than the upper one, but not surprisingly 
for stock has an almost always positive drift rate $\mu$. However, the 
practical probability is even more higher than the upper one at 
`r Prac_Vs_Theo[3, 2]`. This indicates that there is a stronger magnet effect 
when the stock price goes down to approach the lower price limit than the 
upper one. 

We then elaborate to thresholds more adjacent to the price limit, from ±9.0% 
to ±9.9% stepping by 0.1%. As the threshold goes near gradually to the price 
limit, the samlpe size narrows as well, from 128982 to 96176 for the aggregate 
sample (Table \ref{tab:valid_thre_count}).

```{r valid_thre_count}
Valid_Thre_Count %>% 
  kable(caption = "Number of Observations Reaching Different Thresholds", 
        format.args = list(big.mark = ","), 
        booktabs = TRUE) %>% 
  kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

The gap between the practical probability and theoretical probability is 
obvious all the time and, nothing surprising, converges when both probability 
converge to 100% (See Figure \ref{fig:diff_thre}).

```{r diff_thre, fig.height=8, fig.pos="H", fig.cap="Probability to Reach Price Limit from Incremental Thresholds"}
p_Diff_Thre
```


# Further Analysis

We conduct further analysis towards the magnet effect.

## Hard-to-Value Firms

Since the price deviates its inherent traces attracted by the price limit, 
then we should find that the magnet effect is stronger for firms that are 
harder to value.

We use four different measures to proxy for the extent to which a firm is 
difficult to value: firm size, price-to-earnings ratio, whether paying 
dividend and price-to-dividend ratio, with smaller firms, firms that are 
expected to grow more quickly (high price-to-earnings ratio), miser firms 
(paying no dividend), and lower rate of dividend firms being harder to value. 
We do a logistic regression on the probability to reach price limit with each 
hard-to-value measure controling mainly for the theoretical probability. For 
parsimony, we present results only of the aggregate sample, thus we also 
control for the direction since there is much difference between them. 
The logistic regression equation is: 

\begin{equation}\label{eq:hard-to-value}
\begin{split}
Prob(Reaching\ Price\ Limit_{i,t}) &= Logistic(\alpha + \beta\cdot Theoretical\ Probability_{i,t} + \\
&\gamma\cdot Direction_{i,t} + \delta\cdot Hard\ to\ Value\ Measure_{i,t} + \epsilon_{i,t})
\end{split}
\end{equation}

The dependent variable is whether the stock price reaches the price limit. 
Theoretical Probability is from our calulation, Direction is a dummy variable 
indicating the upper direction, Hard to Value Measure takes value from our 
four measures.

Table \ref{tab:hard1} and Table \ref{tab:hard2} present the regression results 
on probability of reaching price limit on each of our four hard-to-value firm 
measures. The Upper dummy controls for a lower gap of the practical 
probability of upper direction. The coefficients of firm size (measured by log 
market value) is −0.034, significant at 1% level, indicating smaller firms 
have a larger probability reaching price limit, controling for the theoretical 
probability. The coefficients of price-to-earnings ratio is 0.055, significant 
at 1% level, indicating firms that are expected to grow more quickly have a 
larger probability reaching price limit. The coefficients of the None-Dividend 
dummy, which indicates that the firm pays no dividend the former fiscal year, 
is 0.114, significant at 1% level, indicating firms that pays no dividend have 
a larger probability reaching price limit. And finally, the coefficients of 
price-to-dividend is 0.018, significant at 1% level, indicating the the lower 
dividend payoff, the larger probability reaching the price limit. All the 
coefficients are significant controling for the direction. As expected, the 
magnet effect is stronger for firms that are harder to value.

```{r hard1, results='asis'}
stargazer(glmfit_S_VAL_MV1, glmfit_S_VAL_MV2, glmfit_S_VAL_PE_TTM1, 
          glmfit_S_VAL_PE_TTM2, 
          title = "Excess Probability Reaching Price Limit with Hard-to-Value Firms", 
          table.placement = "H", 
          dep.var.labels = "Reaching Price Limit", 
          covariate.labels = c("Theoretical Probability", "Upper", "Market Value", 
                               "Price to Earnings"), 
          header = FALSE, 
          label = "tab:hard1", 
          notes.align = "l", 
          notes.append = FALSE, 
          notes = "The table present the results of the logistic regression")
# \\parbox[t]{\\textwidth}{}
```

```{r hard2, results='asis'}
stargazer(glmfit_NON_DIV1, glmfit_NON_DIV2, glmfit_S_PRICE_DIV_DPS1, 
          glmfit_S_PRICE_DIV_DPS2, 
          title = "Excess Probability Reaching Price Limit with Hard-to-Value Firms (Continued)", 
          table.placement = "H", 
          dep.var.labels = "Reaching Price Limit", 
          covariate.labels = c("Theoretical Probability", "Upper", "None-Dividend", 
                               "Price to Dividend"), 
          header = FALSE,
          label = "tab:hard2")
```

\newpage

## Active-Traded Firms

Since the more trade-active stock receive more attention, these stock may be 
push up or down more quickly to the upper or lower price limit. Thus we argue 
that the magnet effect is stronger for more active-traded stocks.

We use trade volume in RMB to measure the trading dynamism. As trade volume 
may be related to firm size, we also use an alternative scaled turnover ratio 
proxy. We run logistic regression on the probability to reach price limit with 
our two stock trading dynamism measures.

\begin{equation}\label{eq:turn}
\begin{split}
Prob(Reaching\ Price\ Limit_{i,t}) &= Logistic(\alpha + \beta\cdot Theoretical\ Probability_{i,t} + \\
&\gamma\cdot Direction_{i,t} + \delta\cdot Trading\ Dynamism\ Measure_{i,t} + \epsilon_{i,t})
\end{split}
\end{equation}

Table \ref{tab:turn} presents the the regression results 
on probability of reaching price limit on our two trading dynamism 
measures. The coefficients of trading volume 
(in RMB) is 0.048, significant at 1% level, indicating more active-trading firms 
have a larger probability reaching price limit, controling for the theoretical 
probability. When it turns to the turnover ratio, the coefficient is 0.120, 
still a significant value at 1% level. All the 
coefficients are significant controling for the direction. 
It indicates that the stocks that gain more trading dynamism may be 
push up or down more quickly to the upper or lower price limit, thus the magnet effect is stronger for them.

```{r turn, results='asis'}
stargazer(glmfit_S_DQ_AMOUNT1, glmfit_S_DQ_AMOUNT2, 
          glmfit_S_DQ_FREETURNOVER1, glmfit_S_DQ_FREETURNOVER2, 
          title = "Excess Probability Reaching Price Limit with Active-Trading Firms", 
          table.placement = "H", 
          dep.var.labels = "Reaching Price Limit", 
          covariate.labels = c("Theoretical Probability", "Upper", "Trading Volume", "Turnover"), 
          header = FALSE, 
          label = "tab:turn")
```

\newpage

## Necessary Triggers

We argur that when the magnet effect takes effect, a trigger is necessary. 
To verify this, we compare our original samlple with that whose obserbations 
have reached the ±9% threshold from right beginning of the market opening, 
that is, the overnight return is beyond ±9%. For this sample, because the 
information is absord for a whole night, and the open price is discretely 
discussed and ascertained from the call auction, it affects much less than 
the sample that has a cross-threshold signal during continuous session.

Table \ref{tab:trigger} presents the difference between the two groups. 
The sample without a trigger has got a much higher 
theoretical probability to `r Trigger_Results_Table[1, 3]` since the 
longer time promises a larger volatility 
arrange. The practical probability comes also a little higher to 
`r Trigger_Results_Table[1, 2]`, however, the 
difference `r Trigger_Results_Table[1, 4]` tends to be insignificant with 
a t-statistic of `r Trigger_Results_Table[1, 5]` and p-value of 
`r Trigger_Results_Table[1, 6]`. This suggests that a signal during 
trading is a necessary trigger for the magnet effect.

```{r trigger}
Trigger_Results_Table %>% 
  mutate_at(vars(`Prac. Prob.`:Diff.), formattable::percent, digits = 1L) %>% 
  kable(caption = "Trigger and Probability of Reaching Price Limit", 
        digits = 1L, 
        format.args = list(big.mark = ","), 
        booktabs = TRUE) %>% 
  kable_styling(latex_options = "HOLD_position")
```

\newpage

# Possible Explanation

For the reason behind the magnet effect, we state that it may be 
caused by liqudity concerns especially by institutional invesetors. When stock 
price reaches price limit, the stock will be no longer tradable (at that 
direction). For that sake, when it approaches the price limit, 
investors may trade it in advance to avoid possible future illiquidity. 
Institutional invesetors who have a more strict trading strategy may meet more 
need to this liqudity concerns. 
We partition our samlpe into quintiles according to institutional ownership. 
In Table \ref{tab:inst} we report the results for the quintiles. With little 
astonishment, firms with more institutional holding have are more stable in 
the long run and have also a lower theoretical probability of reaching the 
price limit. Howerver the practical probability tends to be almost identified 
among all the quintiles. In this way, stocks with higher institutional holding 
tend to be more likely to actually reach the price limit, which in some way 
verifies our conjecture.

```{r inst}
Inst_Results_Table %>% 
  mutate_at(vars(`Prac. Prob.`:Diff.), formattable::percent, digit = 1L) %>% 
  kable(caption = "Institution Holding and Probability Reaching Price Limit", 
        digits = 1L, 
        format.args = list(big.mark = ","), 
        booktabs = TRUE) %>% 
  kable_styling(latex_options = c("HOLD_position"))
```

\newpage

# Conclusion

\vspace{4in}

## References
